stats-project

### 2020-12-04 R - Deliverable/MSDS 6371 - Project.Rmd
add new models

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)

@@

train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  SalePrice)
train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2

@@

test_data_q2 = data_test %>%  select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual,  YearRemodAdd, GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr, Remodel,OverallQual)
test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2

@@

summary(test_data_q2)
#nrow(test_data_q2)
unique(train_data_q2$HouseStyle)
unique(test_data_q2$HouseStyle)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)
library(scales)
library(caret)

@@

train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  SalePrice)
train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2
train_data_q2 = train_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2, SalePrice)

@@

train_data_q2_process = preProcess(train_data_q2[,2:20], method=c("center", "scale"))
train_data_q2 =  predict(train_data_q2_process, train_data_q2)

test_data_q2 = data_test %>%  select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual,  YearRemodAdd, GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr, Remodel,OverallQual)
test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
test_data_q2 = test_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2)
test_data_q2 =  predict(train_data_q2_process, test_data_q2)

@@

summary(test_data_q2)
#nrow(test_data_q2)
unique(train_data_q2$HouseStyle)
unique(test_data_q2$HouseStyle)

```{r}
train_data_q2
test_data_q2
```
